Analysis of Programming Students' Prompts to Identify Interactions Patterns with Generative AI

### 2024-09-16 CSEDU2025/Paper.tex
update

>>>>

% Spacing
Spacing, a well-established learning strategy, was examined by analyzing
 the time intervals between users’ interactions with CharlieBot. Although
 only 12\% of the conversations exhibited message delays exceeding 24 hours,
40\% involved response times longer than 60 minutes. These findings suggest
that students typically do not extend conversations across multiple days.
However, the data also reveal that a substantial number of conversations
feature one or more pauses exceeding an hour, a practice known to enhance
knowledge retention.

% Categories Time
